### 2020-06-09 README.Rmd
readme improvements

The taxize book => <https://taxize.dev>

The functions in the package that work with a specific API have a prefix and suffix separated by an underscore. They follow the format of `service_whatitdoes`.  For example, `gnr_resolve` uses the Global Names Resolver API to resolve species names.  General functions in the package that don't hit a specific API don't have two words separated by an underscore, e.g., `classification`.

You need API keys for Tropicos, IUCN, and NatureServe.

## Currently implemented in `taxize`

>>>>

The taxize book: https://taxize.dev
Package documentation: https://docs.ropensci.org/taxize/

## Data sources currently implemented
